A large-scale analysis of racial disparities in police stops across the

### 2019-07-18 lib/paper_results.Rmd

pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r stop_rates}
pfs$plots$stop
pfs$rates$stop %>% 
  group_by(subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate))
  kable()
```

```{r search_rates}
pfs$plots$search
pfs$rates$search %>% 
  group_by(subject_race) %>%
  summarize(average_search_rate = mean(search_rate))
  kable()
```

>>>>

# pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
# vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
# disp <- read_rds(here::here("results", "disparity.rds"))
# mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```
```{r load_pfs}
# pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
pfs <- read_rds("/share/data/opp/results/prima_facie_stats.rds")
```
```{r load_vod}
# vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
vod <- read_rds("/share/data/opp/results/veil_of_darkness.rds")
```
```{r load_disp}
# disp <- read_rds(here::here("results", "disparity.rds"))
disp <- read_rds("/share/data/opp/results/disparity.rds")
```
```{r load_mj}
# mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
mj <- read_rds("/share/data/opp/results/marijuana_legalization_analysis.rds")
```

@@

```{r stop_rates}
pfs$plots$stop
pfs$rates$stop %>% 
  group_by(subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```

```{r search_rates}
pfs$plots$search
pfs$rates$search %>% 
  group_by(subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```
